Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-31 VMCAI-revised-version/final.tex
effectivity

\begin{proof}
First, note that {\sc Resilience} is undecidable for a Minsky machine $M$ with at least $2$ counters when
$\Safe = \mathop{\downarrow} \Safe$,
since it is possible to have $\Safe = \{q_f(0,0)\}$. 
Now, executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN,dufourd1998reset} in such a way that any sequence 
% from  a state $p({\bf u})$
% to
reaching
 a state 
%
$ q({\bf 0})$ corresponds to one that reaches 
$q_f(0,0)$
 in the Minsky machine and vice versa.
  By combining both constructions, which can be seen in more details in Appendix~\ref{minsk},
 we obtain that 
 {\sc Resilience} is undecidable for reset-VASS when $\Safe = \downarrow \Safe$, and hence for  $\post$-effective, $\pred$-basis-effective, 
$\omega^2$-WSTS with strong compatibility as well.\qed \end{proof}

>>>>

\begin{proof}
First, note that {\sc Resilience} is undecidable for a Minsky machine $M$ with at least $2$ counters when
$\Safe = \mathop{\downarrow} \Safe$,
since it is possible to have $\Safe = \{q_f(0,0)\}$. 
\alain{et alors ? d'où sais-tu que le pb est indécidable pour safe=q,0 ?}
Now, executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN,dufourd1998reset} in such a way that any sequence 
% from  a state $p({\bf u})$
% to
reaching
 a state 
%
$ q({\bf 0})$ corresponds to one that reaches 
$q_f(0,0)$
 in the Minsky machine and vice versa.
  By combining both constructions, which can be seen in more details in Appendix~\ref{minsk},
 we obtain that 
 {\sc Resilience} is undecidable for reset-VASS when $\Safe = \downarrow \Safe$, and hence for  $\post$-effective, $\pred$-basis-effective, 
$\omega^2$-WSTS with strong compatibility as well.\qed \end{proof}
